The Effects of Varying Depth in Cosmic Shear Surveys

### 2019-06-06 paperdraft.tex
Added references

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the Universe. The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Since ground-based surveys are subject to a variation in depth, we investigate and quantify the resulting effects. In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters. Furthermore, we construct COSEBIs of the correlation functions to quantify the occurring B-modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$. However, the parameter $S_8$ is robust against this modification. We find that the dependency of this effect on the underlying cosmology is not negligible. We also report the occurrence of B-modes, although not at a significant level.
% conclusions (optional)
   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments. Due to the cosmology dependency, further analyses require a fast, analytic model for this effect.}

@@

For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}. With next-generation surveys like the Large Synoptic Survey Telescope and Euclid \todo{Could someone please point me to papers to cite for these surveys?} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}. %\todo{Citations.. \citet{2017MNRAS.464.1676A} has a few...}

@@

Assuming that the depth, and thus the source redshift populations, varies between pointings, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
In accordance to the definition of the shear power spectrum \begin{equation}
\la \hat{\gamma}(\b\ell)\,\hat{\gamma}^*(\b\ell')\ra = (2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) \, ,
\end{equation}
we define the observed power spectrum via \begin{equation}
P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell)\, \gammaoh {}^*(\b \ell')\ra \, .
\end{equation}
Here, and throughout the rest of this paper, $\hat{\gamma}$ denotes the Fourier transform of $\gamma$. Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as 
\begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases},
\label{eq:defweightf}
\end{equation}
where $L$ is the length of one pointing.
Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
\begin{equation}
P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)\, P(\b k)\, ,
\end{equation}
where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function and $\hat{\Xi}$ is the Fourier transform of a box-function, which is a 2-dimensional sinc-function (compare \ref{sec:calc of PS}).
The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$. In particular, the power spectrum is not isotropic anymore.

@@

However, we will now derive a more sophisticated model that includes the effects of the LSS. While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
%-------------------------------------------------
%Given a set of average redshifts, following \citet{2006APh....26...91V}, we can estimate 
%\[
%\la |\gamma| \ra \propto \la z \ra ^{0.85}\, .
%\]
%We shall later see that this approximation is valid for higher tomographic redshift bins $z\gtrsim 0.5$, but starts to break down at lower redshifts. We thus want to construct a model that is valid for an arbitrary distribution of redshifts and does not rely on the assumption of a single lens plane. 
\subsection{Using a semi-analytic Model}
\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17. Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}. Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}. Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution. For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17). If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions. Formally, we define \[
\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} P_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} P_{mn}^{ij}(\theta)}\, ,
\label{eq:def_xiobs}
\]
where $P_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth. We will later discuss the validity of these assumptions as well as possible mitigation strategies.

To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky. For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile. The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$. Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$. The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$. The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$. We get for $n\neq m$: \[
\mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
\label{eq:pmnij_corr1}
\]
For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile. We therefore set \[
\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
\label{eq:pmnij_corr2}
\]
We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
\label{eq:pmnij_uncorr}
\]
where $\delta_{mn}$ denotes the Kronecker delta.
Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
\begin{align}
\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
\]
A more mathematically rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.

@@

\section{Results}
\label{sec:results}
We applied both our methods to data from the KV450 survey and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some specifications of the KV450 survey here, like introduce the tomographic bins, etc. Or could I just link to Hendrik's paper?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles. For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution. Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included). This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, is this what you did? If you are unhappy with any of these explanations, or feel like I missed something, please feel free to add it :)}. As in \citet{2018arXiv181206076H}, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins. The result can be seen in Figure \todo{For the analytic model, describe how we get to $W$ (either van Waerbecke (2006) or taking a value of $\xi_\pm$.}\ref{fig:all_xis}.
	\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
	\caption{The ratio of observed to modeled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins. The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}
	\label{fig:all_xis}
	\end{figure}
We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge. We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk? Maybe in the appendix to avoid too many Figures?}\footnote{We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect: Following Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function. This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$. However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum. A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}

>>>>

  \abstract
% context (optional)
   {Cosmic shear proves to be a powerful tool to study the properties of the Universe. The discrepancy in the parameter $S_8 = \sigma_8\sqrt{\Omega_{\rm{m}}/0.3}$ between measurements in the local Universe and the Cosmic Microwave Background motivates further investigation of yet unaccounted systematic biases. 
% aims
   Since ground-based surveys are subject to a variation in depth, we investigate and quantify the resulting effects. In particular, we check whether they introduce a bias to the resulting cosmological parameters and if they can be responsible for the occurrence of B-modes.
% methods
   We construct a semi-analytic model to estimate the impact on the shear correlation functions and analyse the implications for cosmological parameters. Furthermore, we construct COSEBIs of the correlation functions to quantify the occurring B-modes.
% results
   For the Kilo-Degree Survey this effect introduces an error in $\xi_\pm$ of the order of a few percent on small scales, which is responsible for a $0.1\sigma$ bias in $\Omega_{\rm m}$ and $\sigma_8$. However, the parameter $S_8$ is robust against this modification. We find that the dependency of this effect on the underlying cosmology is not negligible. We also report the occurrence of B-modes, although not at a significant level.
% conclusions (optional)
   We conclude that the effects of varying depth for ground-based surveys on cosmological parameters are not yet significant, but should be accounted for in next-generation experiments. Due to the cosmology dependency, further analyses require a fast, analytical model for this effect.}

@@

For current cosmic shear surveys, the estimated systematic error is of comparable size to the statistical error, implying that for next-generation surveys, a significant reduction of systematic errors is necessary \citep[compare][hereafter H17]{2017MNRAS.465.1454H}. With next-generation surveys like the Large Synoptic Survey Telescope\citep{Ivezic:2008} and Euclid\citep{Laureijs:2011} soon to start, systematic effects in gravitational lensing have received a large amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}. %\todo{Citations.. \citet{2017MNRAS.464.1676A} has a few...}

@@

Assuming that the depth, and thus the source redshift populations, varies between pointings, an observer will measure a shear-signal that is modified by a step-like depth-function $\gammao(\b\theta)=W(\b \theta)\gamma(\b\theta)$, where $W$ is proportional to the mean of the lensing efficiency $\Dds/\Ds$ of one pointing and $\gamma$ denotes the shear that this pointing would read if it were of average depth.
We can parametrize $W$ as $W(\bm{\theta}) = 1+w(\bm{\theta})$, where $\langle w(\bm{\theta})\rangle=0$ holds. 
In accordance to the definition of the shear power spectrum \begin{equation}
\la \hat{\gamma}(\b\ell)\,\hat{\gamma}^*(\b\ell')\ra = (2\pi)^2\delta(\b\ell-\b\ell')P(|\b\ell|) \, ,
\end{equation}
where $\hat{\gamma}$ denotes the Fourier transform of $\gamma$, we define the observed power spectrum via \begin{equation}
P^{\text{obs}}(\b\ell) \equiv \frac{1}{(2\pi)^2}\int \d^2 \ell'\,  \la \gammaoh(\b \ell)\, \gammaoh {}^*(\b \ell')\ra \, .
\end{equation}
Note that due to the depth-function both the assumptions of homogeneity and isotropy break down, which means that we can neither assume isotropy in the power spectrum, nor can we assume that $\la \gammaoh(\b \ell) \gammaoh {}^*(\b \ell')\ra$ vanishes for $\b\ell\neq\b\ell'$.
To model a constant depth on each individual pointing $\b \alpha$, we can choose random variables $w_{\b \alpha}$, that only need to satisfy $\langle w_{\b \alpha}\rangle=0$, and parametrize $w(\b\theta)$ as 
\begin{equation}
w(\b \theta) = \sum_{\b \alpha \in \mathbb{Z}^2} w_{\b \alpha} \Xi(\b \theta-L\b \alpha)\text{ , with the Box-Function } \Xi(\b \theta) = \begin{cases}
1 \qquad \b \theta\in \left[-\frac{L}{2},\frac{L}{2}\right]^2 \\
0 \qquad \text{else}
\end{cases},
\label{eq:defweightf}
\end{equation}
where $L$ is the length of one pointing.
Following the calculations in Appendix \ref{sec:calc of PS}, we derive 
\begin{equation}
P^{\text{obs}}(\b \ell)  =  P(\b \ell) + \la w^2\ra \int\frac{\text{d}^2\b k}{(2\pi)^2}\,\hat{\Xi}(\b \ell-\b k)\, P(\b k)\, ,
\end{equation}
where $\la w^2\ra \equiv \la w_{\b \alpha}^2\ra$ is the dispersion of the depth-function and $\hat{\Xi}$ is the Fourier transform of a box-function, which is a 2-dimensional sinc-function (compare \ref{sec:calc of PS}).
The observed power spectrum $P^{\text{obs}}$ is thus composed of the original power spectrum $P$, plus a convolution of the power spectrum with a sinc-function, scaling with the variance of the function $w(\b\theta)$. In particular, the power spectrum is not isotropic anymore.

@@

However, we will now derive a more sophisticated model that includes the effects of the LSS. While it is computationally more expensive, it yields accurate results for cosmic shear surveys, which are sensitive to the exact redshift distributions of sources as well as the underlying cosmology.
%-------------------------------------------------

\subsection{Using a semi-analytic Model}
\label{sec:xipm_semianalytic}
\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17. Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}. Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}. Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution. For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17). If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions. Formally, we define \[
\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)}\, ,
\label{eq:def_xiobs}
\]
where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth. We will later discuss the validity of these assumptions as well as possible mitigation strategies.

To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky. For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile. The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$. Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$. The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$. The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$. We get for $n\neq m$: \[
\mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
\label{eq:pmnij_corr1}
\]
For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile. We therefore set \[
\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
\label{eq:pmnij_corr2}
\]
We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
\label{eq:pmnij_uncorr}
\]
where $\delta_{mn}$ denotes the Kronecker delta.
Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
\begin{align}
\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
\]
A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.

@@

\section{Results}
\label{sec:results}
We want to apply both methods to data from the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018}. While the application of the semi-analytic method is straightforward, for the analytic method we need to decide how to estimate the weight function $W$ from given redshift data. Following the separation of a survey into percentiles as in Sect. \ref{sec:xipm_semianalytic}, we define $W(\b\theta)\equiv W_n$ whenever $\b\theta$ is in a pointing of percentile $n$. For the determination of $W_n$ we tried two approaches:
 As a first method, following \citet{2006APh....26...91V}, we estimate 
\[
W_n \propto \la z_n \ra ^{0.85}\, ,
\]
where $\la z_n\ra$ is the average redshift of percentile $n$. As a second method we define \[
W_n \propto \la\gamma_{\rm{t}}\gamma_{\rm{t}}\ra (\theta') + \la \gamma_\times\gamma_\times\ra (\theta') = \sqrt{\xi_{+,nn}^{ij}(\theta')}\, ,
\]
\todo{Maybe we set $W_n\propto \sqrt[4]{\la \gamma_t\gamma_t\ra^2 + \la \gamma_\times\gamma_\times\ra^2 } \propto \sqrt[4]{\xi_+^2 + \xi_-^2}$?}
where the $\xi_{+,nn}^{ij}(\theta')$ denotes the model correlation function defined in Sect. \ref{sec:xipm_semianalytic}, evaluated at a characteristic scale $\theta'$.

While the first method suffers from the fact that the power-law index is redshift-dependent, the second method is sensitive to the angular range $\theta$, at which the shear correlation functions are evaluated, which is completely arbitrary.

We applied both analytic methods and the semianalytic one to data from the KV450 survey, following the separation into tomographic bins as in H18, and computed the ratio of observed and modeled correlation functions.\todo{Probably I should include some more specifications of the KV450 survey here?} Furthermore, we conducted numerical simulations investigating the same issue: A $100\,\rm{deg}^2$ field in the Scinet Light Cone Simulations (SLICS) \citep{2018MNRAS.481.1337H} was randomly separated into 10 percentiles. For each tomographic redshift bin of each percentile, galaxies were placed to trace the respective redshift distribution. Afterwards, their expected shear was determined (shape-noise in the form of intrinsic ellipticities of galaxies was not included). This was compared to a set of simulations where the galaxies were simply distributed according to the combined redshift distribution of each respective tomographic bin\todo{Catherine, I feel like I am grossly oversimplifying what you did. Maybe you could write a short paragraph about the simulations?}. As in H18, we have separated the data in 5 tomographic redshift bins and performed our analysis for a cross-correlation of all bins. The result can be seen in Fig.~\ref{fig:all_xis}.
	\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{images/allxis_0111.pdf}
	\caption{The ratio of observed to modelled correlation functions for the analytic method (green), the semi-analytic method (blue) and the numerical simulations (red) for a cross-correlation of all redshift bins. The numbers in the upper left corners correspond to the respective redshift bins, the upper left triangle depicts the ratios of $\xi_+$, whereas the lower right triangle depicts the ratios of $\xi_-$.}
	\label{fig:all_xis}
	\end{figure}
We can see that for high redshift bins, the analytic and the semi-analytic methods are consistent, whereas for low redshift bins they significantly diverge. We explain this due to the facts that the analyic method uses simplifications that are redshift-dependent and only hold for small variations in redshift, which is not fulfilled in the low redshift bins.\todo{Should I include the plot number density vs average redshift from the talk? Maybe in the appendix to avoid too many Figures?}\footnote{We also observe that in the semi-analytic model, $\xi_-$ seems to be much stronger affected by this effect: Following Equation \eqref{eq:xipm-pkappa}, $\xi_+$ is computed by filtering the power spectrum with the 0-th order Bessel function. This function peaks at $\ell\theta=0$, meaning that for all values of $\theta$, the correlation function $\xi_+$ is sensitive to small values of $\ell$, corresponding to large separations $\theta$. However, $\xi_-$ is obtained by filtering with the 4-th order Bessel function, which peaks at approximately $\ell\theta\approx 5$, so for different $\theta$ this function is sensitive to varying parts of the convergence power spectrum. A more detailed analysis of this can be found in the Appendix of \citet{2017MNRAS.471.4412K}.}
